\textsf{Are large language models superhuman chemists?}

### 2024-03-24 src/tex/ms.tex
Update ms.tex

\paragraph{Question selection} \label{sec:subset-selection}
Since we anticipated that we will not be able to collect enough responses for every question to allow for a meaningful statistical analysis, we decided on showing a relevant subset of all questions to the human scorers.
For selecting the subset, we decided on addressing two questions:
\begin{itemize}
    \item Are the questions for which the models scored poorly just too difficult or unanswerable?
    \item Are there areas in which the performance of humans is very different from the ones of the models?
\end{itemize}
To answer the first question we selected up to 13 questions per source that all \glspl{llm} (model names) from an initial scoring round did not answer correctly.
In addition, we picked 100 diverse one using greedy MaxMin sampling on the embeddings on the questions computed using BART and added five random questions about the number of \gls{nmr} peaks and the point group of molecules.
% https://github.com/lamalab-org/chem-bench-app/issues/92 has the details

>>>>

\paragraph{Question selection} \label{sec:subset-selection}
Since we anticipated that we will not be able to collect enough responses for every question to allow for a meaningful statistical analysis, we decided on showing a relevant subset of all questions to the human scorers.
For selecting the subset, we decided on addressing two questions:
\begin{itemize}
    \item Are the questions for which the models scored poorly just too difficult or unanswerable?
    \item Are there areas in which the performance of humans is very different from the ones of the models?
\end{itemize}
To answer the first question we selected up to 13 questions per source that all \glspl{llm} (model names) from an initial scoring round did not answer correctly.
In addition, we picked 100 diverse ones using the greedy MaxMin sampling on the embeddings of the questions computed using BART and added five random questions about the number of \gls{nmr} peaks and the point group of molecules.
% https://github.com/lamalab-org/chem-bench-app/issues/92 has the details
